### 2019-06-10 2-Chapters/3-Chapter/chapter3.tex
Typeset unit (B, KiB, s, µs) correctly, thanks to siunitx

We have been able to check empirically that the regret of all the efficient algorithm indeed scales as predicted by the theory, that is
linearly in the number of arms, and logarithmically in the horizon, \ie, $R_T = \bigO{K \log T}}$.
%
The main take-away message is the following: in all the rest of this thesis, we focus on two algorithms depending if simplicity or efficiency is favored:
\begin{itemize}\tightlist
    \item
    \UCB{} is used in the more applied Chapter~\ref{chapter:4}, when simplicity is favored,
    \item
    \klUCB{} is used, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}, when efficiency is favored.
\end{itemize}

>>>>

We have been able to check empirically that the regret of all the efficient algorithm indeed scales as predicted by the theory, that is
linearly in the number of arms, and logarithmically in the horizon, \ie, $R_T = \bigO{K \log T}$.
%
The main take-away message is the following: in all the rest of this thesis, we focus on two algorithms depending if simplicity or efficiency is favored:
\begin{itemize}\tightlist
    \item
    \UCB{} is used in the more applied Chapter~\ref{chapter:4}, when simplicity is favored,
    \item
    \klUCB{} is used, in the two more theoretical Chapters~\ref{chapter:5} and \ref{chapter:6}, when efficiency is favored.
\end{itemize}

### 2019-06-10 2-Chapters/4-Chapter/chapter4.tex
Typeset unit (B, KiB, s, µs) correctly, thanks to siunitx

We present in Section~\ref{sec:4:firstModel} how the MAB algorithms can be used in a unlicensed but frequency- and time-slotted IoT network.
Several devices are using bandit algorithms, and the assumptions made by the stochastic bandit algorithms are not satisfied: as several agents learn simultaneously and their activation processes are random, their behavior is not stationary.
As far as we know, we provide the first practical study to confirm robustness of the use of stochastic bandit algorithms for decision making in IoT networks with a large number of intelligent devices in the network, which makes the environment ``highly not stationary''.
This specific context makes it very hard to give mathematical proofs of  convergence and efficiency for bandit algorithms (that is why we relax the hypothesis and only consider up-to $M\leqK$ players in Chapter~\ref{chapter:5}).
We then validate the model with a hardware implementation on real radio signals, detailed in Section~\ref{sec:4:gnuradio}.
%
We conclude this chapter by presenting in Section~\ref{sec:4:retransmissions} an extension of this model to take into account another aspect of the ALOHA protocol, that is the possibility for dynamic devices to retransmit their packet if the \emph{Ack} was not received.

>>>>

We present in Section~\ref{sec:4:firstModel} how the MAB algorithms can be used in a unlicensed but frequency- and time-slotted IoT network.
Several devices are using bandit algorithms, and the assumptions made by the stochastic bandit algorithms are not satisfied: as several agents learn simultaneously and their activation processes are random, their behavior is not stationary.
As far as we know, we provide the first practical study to confirm robustness of the use of stochastic bandit algorithms for decision making in IoT networks with a large number of intelligent devices in the network, which makes the environment ``highly not stationary''.
This specific context makes it very hard to give mathematical proofs of  convergence and efficiency for bandit algorithms (that is why we relax the hypothesis and only consider up-to $M \leq K$ players in Chapter~\ref{chapter:5}).
We then validate the model with a hardware implementation on real radio signals, detailed in Section~\ref{sec:4:gnuradio}.
%
We conclude this chapter by presenting in Section~\ref{sec:4:retransmissions} an extension of this model to take into account another aspect of the ALOHA protocol, that is the possibility for dynamic devices to retransmit their packet if the \emph{Ack} was not received.
